Example use of prediction functions

### 2017-09-01 function_demonstration.Rmd
added code to demonstrate how to use plot_failure function

This markdown demonstrates how to use functions fit_model, variable_setup and predict_failure to get failure probability predictions for questions posted on iFixit's Answers forum.

@@

>>>>

This markdown demonstrates how to use fit_model, variable_setup, predict_failure and plot_failure to get failure probability predictions for questions posted on iFixit's Answers forum, and plot the failure probability curves for specific questions.

@@

##### plotting predicted failure probabilities for specific questions

```{r}
# plotting the failure curve for the first question of the prediction data
question <- for_predict[1,]
oshitar::plot_failure(model, question)
```

```{r}
# plotting the failure curve for the 50th question of the prediction data
question50 <- for_predict[50,]
oshitar::plot_failure(model, question50)
```
